\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[a4paper,left=1.2cm,right=1.2cm,top=1.2cm,bottom=1.2cm]{geometry}
\usepackage{xcolor}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{tabularx}
\definecolor{accent}{HTML}{1F4E79}
\setlength{\parindent}{0pt}
\setlist[itemize]{left=0pt,label=--,topsep=0pt,parsep=0pt,itemsep=0.3em}
\titleformat{\section}{\Large\bfseries\color{accent}}{}{0pt}{}
\titleformat{\subsection}{\bfseries}{}{0pt}{}
\begin{document}
\noindent{\color{accent}\Huge\bfseries Lucas Lousada}\\[0.5em]
\noindent{\Large Linux specialist \& technical customer support leader}\\[1em]
\section*{Contact}
\begin{tabularx}{\linewidth}{@{}X X@{}}
\textbf{Email:} & \href{mailto:lucas.mlousada@gmail.com}{lucas.mlousada@gmail.com}\\
\textbf{Location:} & Dalkeith, Scotland, UK\\
\textbf{LinkedIn:} & \href{https://www.linkedin.com/in/lucas-mlousada/}{linkedin.com/in/lucas-mlousada}\\
\end{tabularx}
\section*{Technical toolkit}
\begin{itemize}
  \item Linux / Debian / Slackware
  \item Kubernetes / Containers
  \item RING / Artesca / S3 API
  \item Veeam / Commvault / Rubrik
  \item Ansible / Salt / Bash / Python
  \item Grafana / Prometheus / Alertmanager
  \item Kafka / Keycloak / HTTP / TCP/IP
  \item Samba / NFS / Backup / Monitoring
  \item Customer success / escalation
\end{itemize}
\section*{Languages}
Portuguese; English\\[0.8em]
\section*{Core strengths}
\begin{itemize}
  \item Reliable Linux operations at scale
  \item Cross-team technical enablement
  \item Customer-facing incident response
  \item Documentation and onboarding
  \item Complex system troubleshooting
\end{itemize}
\section*{Summary}
{\large I deliver resilient Linux infrastructure and practical support for enterprise storage systems. With 15+ years of hands-on Linux experience, I translate architecture and observability into actionable outcomes for customer success and engineering collaboration.}\\[1em]
\section*{Experience}
\subsection*{Service and Support Engineer, Scality \textnormal{(May 2020 -- Present)}}
\begin{itemize}
  \item Maintain RING and Artesca production software, driving issue resolution between customers and engineering.
  \item Author troubleshooting guides, technical runbooks, and process documentation.
  \item Serve as a customer advocate for product quality, integrations, and supportability.
  \item Troubleshoot S3 storage, backup integrations, networking, and Linux service issues.
  \item Support container deployments and automation using Ansible and Salt.
  \item Deliver observability support for Grafana, Prometheus, Alertmanager, Keycloak, and Kafka.
\end{itemize}
\subsection*{Linux SysAdmin, Collabora \textnormal{(July 2019 -- May 2020)}}
\begin{itemize}
  \item Managed Linux infrastructure with Chef automation for collaboration and developer tool services.
  \item Delivered technical support across Debian-based deployments, Git workflows, email, and file systems.
  \item Coordinated support between technical teams and external customers.
\end{itemize}
\subsection*{Technical Support Engineer, nCipher Security \textnormal{(Jan 2019 -- July 2019)}}
\begin{itemize}
  \item Supported nShield cryptography hardware and software in customer environments.
  \item Investigated hardware, software, and network faults, liaising with engineering teams.
\end{itemize}
\subsection*{Technical Support Engineer, Thales eSecurity \textnormal{(Sep 2018 -- Dec 2018)}}
\begin{itemize}
  \item Provided customer support for cryptographic security products.
  \item Created escalation-ready diagnostics and product optimisation guidance.
\end{itemize}
\subsection*{Technical desk agent, Hive | Centrica Connected Home \textnormal{(July 2017 -- Sep 2018)}}
\begin{itemize}
  \item Monitored AWS systems using CloudWatch, Wavefront, and Kibana.
  \item Automated operational workflows and managed incident tracking in Jira.
\end{itemize}
\subsection*{IT Support Analyst III, Nube \textnormal{(July 2011 -- June 2017)}}
\begin{itemize}
  \item Built and supported a Slackware distribution for 300 employees.
  \item Implemented monitoring with Nagios, Cacti, OSSEC, and OCS.
  \item Delivered internal training and secure remote access solutions.
\end{itemize}
\subsection*{COBOL Developer, BSI Tecnologia / Unibanco AIG \textnormal{(May 2007 -- Nov 2008)}}
\begin{itemize}
  \item Migrated legacy COBOL systems and standardized applications for modern platforms.
\end{itemize}
\section*{Education}
\textbf{Universidade Presbiteriana Mackenzie}\\
Bachelor's degree in System, Networking and LAN/WAN Management\\
2007 -- 2014
\section*{Selected projects}
\begin{itemize}
  \item Delivered a bespoke Slackware distribution for enterprise adoption and training.
  \item Integrated observability and backup systems for infrastructure reliability.
  \item Guided customers through secure storage deployments, troubleshooting, and performance tuning.
\end{itemize}
\end{document}
